---
title: "Eating Out"
author: "Alondra Cruz"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Is there a difference between various ethnicities and the prevalence of eating out. 

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```
# Method
Race is the categorical variable and how often they eat out is numerical. We have a Cat ~ Num. 

# Descriptive Results


## Graphical Results


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

These barcharts suggest that there is a small difference between the ethnicites and eat out.

# Numerical Description

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The numerical description tests show that white eat out more frequently than black or other races. 

## Infrential 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```

The p-value 0.001208 is so small that I reject the null hypothesis. Therefore there is a difference among eating out based off race. 

# Discussion and Conclusion

Is there a difference between the frequency of eating out based of race, based off the Fisher's Exact Test we found that there is a difference between eating out and race. The test show that whites eat out more frequently than blacks and other races. 
